Do I Need to Model You in order to Learn With You?

### 2015-04-02 mutual-modeling.tex
Work on studies section -- WIP

@@

We could go further by comparing self- versus other modelling ($\Delta_4$ in
Fig.~\ref{mm_rectangle}) as an indication of meta-cognitive skills. We can also
question if modelling skills depend upon what aspects are being modeled ($X$ or
$Y$), which would explain vertical differences ($\Delta_5$ in
Fig.~\ref{mm_rectangle}). We do not however further explore these questions
since we do not have the necessary data in our studies.

@@

We studied the impact of an awareness tool on group performance and mutual
modelling~\citep{nova2007collaboration}. The availability
of an awareness tool was our independent variable. In previous studies, we
replayed a video of the game to subjects who surprised us by their ability to
remember former states of their mutual model: ``I did that because I thought that
you would do that''. Hence, this experiment focused the representation of each
other's action plans. During the game, we asked them to anticipate the next
action of their partner as well as to announce their own action. It is clear
asking them a question about their partner increases their attention for the
rest of the game.

@@

SpaceMiners is a 3D game that involves two players collecting minerals located
in asteroids (Fig.~\ref{study1:spaceminer}). To do so, they shoot drones through
the space after choosing their initial direction and speed. Once launched, the
trajectory of drones is only influenced by the gravity of planets and by
trajectory modification tools.  During the experiment, the teams were confronted
with three increasingly complex situations. The experiment was 2 hours long: a
30 minutes tutorial and 3 levels of 30 minutes. Players uses using a regular
joystick and communicated with each other through an audio channel.

@@

Thirty-six persons participated in this study, all native French speakers. We
constituted 18 pairs of participants (N = 18) who were not familiar with each
other. The pairs were assigned randomly to either the control condition (without
the awareness tool) or the awareness condition (with the awareness tool).

\begin{figure*}
        \centering
        \includegraphics[width=0.9\textwidth]{image4.png}
        \caption{Snapshot of the SpaceMiner Game}
        \label{study1:spaceminer}
\end{figure*}

@@

Task performance was measured by the score reached by the two subjects after
three situations. The effort of mutual modelling was measured as the ratio of
time that players would spend in the scout mode (divided by total time), which
is the time during which players are not performing their own actions but
monitoring their partner's actions.

In order to evaluate \gModel{A}{B} during the task, we used two questionnaires
(Fig.~\ref{study1:questionnaires}) that were displayed during each of the three
games, as a transparent layer appearing over the game display. The first
questionnaire concerned the player's intended actions. The second questionnaire
asked each player about what he thought her or his partner was intending to do.
Some answers were identical in both questionnaires (like ``adjusting a shot'')
while others were reversed (``to guide my partner'' versus ``to guide me''). We
chose this subjective measure of accuracy ($\Delta(\M{A}{B}{x}, \M{B}{B}{x})$)
rather than an objective measure (\ie the model \gmodel{A}{B} is compared to $B$'s
next action) because some the activities proposed by the questionnaire were not
observable by the environment (\eg establishing a strategy). We counted
\Model{A}{B}{activity_{game_{i}}}) as the number of common answers between
questionnaires \gmodel{A}{B} and \gmodel{B}{B} in each game and computed the
average value a across the 3 games.

@@

\paragraph{Study-specific questions} The awareness tool permitted higher group
performance, but it did not improve the accuracy of the mutual model. Since
teams were free to use the awareness tool or not (the \emph{scout} mode), we
performed a post-hoc split of players depending on how much time they used it.
The split point was the mean of time spent in the scout mode and it led to the
constitution of two groups made up of 12 individuals ``short time in scout
mode'' and 24 individuals ``long time in scout mode''. A two-way analysis of
variance conducted on these contrasted groups revealed that pairs in the
awareness condition who spent more time in the scout mode reached higher levels
of \gModel{A}{B}($F = 8.02, p = 0.015$). Of course, a \textit{post-hoc} split
does not support a causal direction. An alternative explanation could be that
good modellers are more social and hence appreciate the awareness tool.

@@

\paragraph{Triangle questions} We cannot answer the triangle questions since
this study was conducted with dyads.

@@

This study concerns a collaborative game that occurred in the physical
space~\citep{nova2006underwhelming}. We studied whether players build an accurate
model of the path followed by their partners because this path reflected their
problem solving strategy. We used an objective measure of \gModel{A}{B}: the
distance between where $A$ believes $B$ has been walking and where $B$ actually went.
The main hypothesis concerned the effect of awareness tools on group performance
and on \gModel{A}{B}.

@@

{\sc CatchBob} is a mobile game in which groups of 3 players have to solve a
joint task. The game was played on EPFL campus. Participants had to find a
virtual object (\emph{Bob}) and ``to catch it'' by forming a triangle around it.
Players used a Tablet PC that displayed a map of the campus and an indication of
their personal distance to Bob. Their annotations on the map were shared with
the two other players ($A$ could see what $B$ and $C$ wrote). These annotations faded
out after a few minutes to avoid covering the full display. The awareness tool
displayed as well the location of the two other players on the map. The
availability of location awareness tool constituted our independent variable.

@@

Ninety students participated in this experiment. We chosen only students from
our university because knowing the campus geography had an impact both on group
performance but also on mutual modelling: it is hard to represent the path of
someone across some space without having a mental map of this space. We selected
groups of students who knew each other. We assigned 10 triads to each of our
three experimental conditions. Each condition was made up of approximately 25\%
of women, but we did not control gender repartition within each triad.

@@

The independent variable was the awareness tool: the control condition (without
tool) and two experimental conditions: synchronous awareness (display current
position of each player) and asynchronous awareness (display current position of
each player and their recent spatial trace).  As a dependent variable, we had
the task performance which was the distance covered by the team to catch Bob and
\gModel{A}{B}. To estimate \gModel{A}{B}, we asked players to draw on paper
their own path and the path of each of their partners after the game. This
enabled us to calculate the number of errors players made while drawing the path
of their partners. We compared the path that player $A$ attributed to $B$ with $B$'s
real path recorded by the system and the same for $A$ \& $C$ and $B$ \& $C$ as depicted
on Fig.~\ref{study2:paths}.

@@

\paragraph{Study-specific questions} There was no significant difference
regarding the task performance. However, our surprise was that the absence of
the awareness tool was related to a higher \gModel{A}{B}: players better
remembered their partners' path if they did not see their position permanently!
We will not enter into the details of these results but, to be short, teams
without awareness tool made more annotations on the map while permanent MLA has
an underwhelming effect~\citep{nova2005location}.

\paragraph{Symmetry question} The correlation between \gModel{A}{B}  and
\gModel{B}{A}  is positive ($r = .41$) and significant ($p < .01$);  the more A
makes errors about $B$, the more $B$ does the same.

\paragraph{Triangle questions} Regarding $\Delta_2$, the correlation between
\gModel{A}{B} and \gModel{A}{C} is significant: $r=0.30, p <.01$. Concerning
$\Delta_3$, the correlation between \gModel{A}{C} and \gModel{B}{C} is
significant as well: $r=0.43, p <.001$.

@@

This positive result regarding to the symmetry question is even more surprising
than the previous one: despite the high heterogeneity of spatial skills among
adults~\citep{liben1981spatial}, a significant correlation could indicate that
mutual modelling relies more on group processes than on individual processes. The
significant results on the triangle questions probably go in the same direction:
either the modeler or the modeled both contribute to accurate modelling, or that
the quality of teamwork has a global effect. In this experiment, since team
members did not interact intensively during the task, the factor that
facilitates accurate mutual modelling is probably less the quality of verbal
interactions that the group strategy: a clear strategy facilitates memorizing
one's partner path.

@@

\begin{figure*}[ht!]
        \centering
        \includegraphics[width=0.9\textwidth]{image8.jpg}
        \caption{Example of argumentation graph}
        \label{study3:argumentation_graph}
\end{figure*}

@@

Triads had to address an emotional societal debate: authorizing or not adoption
by homosexual couples. They worked on-line and had to structure their
argumentation with a shared concept map tool {\sc TeamWave} as illustrated in
Fig.~\ref{study3:argumentation_graph}. Ten groups had only an audio connection
while ten groups had audio plus video. The video communication was provided by a
web cam and the software {\sc IVisit}. For the audio link, we used microphones,
headsets and a software called {\sc BattleCom}. In the audio+video condition,
the screen was divided in three sections. The main part was devoted to the
concept map window (24x24cm). In the remaining part appeared the image of the
two peers (8.5x8.5cm each). In the audio condition, this video zone was left
empty so that the size of the concept map was equal in each condition. The
subjects were located in the same room, separated by mobile walls. Despite their
headsets, it is not impossible that they could hear non-verbal audio cues (\eg
tapping the sole with feet).  The task last in average 61 minutes.

@@

Twenty triads from the University of Geneva participated to this experiment. We
formed groups of subjects who knew each other, \ie they had \emph{ab initio}
mutual models: the task required the discussion of sensitive issues which
required to feel quite comfortable with peers. There were 36 women and 24 men,
but, since groups were formed a priori, we could not control the balance of men
and women in each condition.

@@

The independent variable was the presence of not of video link. The dependent
variable \gModel{A}{B} was subjectively by using 3 questionnaires: in the first
one, $A$ described his or her own emotions \gmodel{A}{A} , while in the two other
questionnaire, $A$ describes $B$'s and C's emotions. The questionnaire included 18
items (7-point Likert Scale) describing emotions labeled as adjectives:
\emph{anxious}, \emph{enthusiastic}, \emph{agitated}, \emph{proud},
\emph{excited}, \emph{quiet}, \emph{calm}, \emph{stressed}, \emph{bored},
\emph{upset}, \emph{relaxed}, \emph{irritated}, \emph{determined},
\emph{hostile}, \emph{active}, etc. This list of emotions was
elaborated from \fixme{REF?}. The proposed emotions were \fixme{?}. \gmodel{A}{B} is a vector
of 18 numerical values ${x_1 \dots x_i}$ corresponding to their answers on each
questionnaire. \gModel{A}{B} has been computed as the correlation between the
two vectors (Eq.~\ref{eq:study3}).

\begin{multline} \label{eq:study3}
    \Mdeg{A}{B}{emotions}\\
    = \Delta(\M{A}{B}{\{x_1 \dots x_i\}}, \M{B}{B}{\{y_1 \dots y_i\}}) \\ 
    = r(\{x_1 \dots x_i\}, \{y_1 \dots y_i\})
\end{multline}

@@

\paragraph{Grounding criterion} The maps produced by teams were ranked. We use
the average rank as a estimation of the team performance and correlated with the
average of the 6 values of \gModel{A}{B} per team (\gModel{A}{B}, \gModel{A}{C},
\gModel{B}{A},...): The correlation is -0.22: teams with a good \gModel{A}{B}
team to be better ranked.

@@

\paragraph{Triangle questions} \fixme{Check ($\Delta_2$)} For $\Delta_3$, if we
compute for each subject A, the correlation between the vectors of emotions in
\gmodel{B}{A} and the vector in \gmodel{C}{A}, and take the average across all
60 subjects, we obtain a very impressive correlation of .66. This average is
about the same in each condition.

\paragraph{Rectangle question} We cannot address the relationship ($\Delta_4$)
between self-and social accuracy here because we don't have an estimation of
self-accuracy: subjects describe their emotions but we have no way to check if
there are correct. However, by measuring \gModel{A}{B} on  18 emotional labels,
we can however have a glimpse about $\Delta_5$: how \Model{A}{B}{X} varies
according to X.  Fig.~\ref{study3:deg_m_values} shows the range of modelling
errors: the difference between \gmodel{A}{B} and \gmodel{B}{A}, on a scale of 7,
is in average of 0.3 for the emotion \emph{discasted}, and up to 1.9 for the
emotion \emph{calm}. This is probably specific to the variety of scales  ($SD=
0-5$ for \emph{discated} versus $SD=.7$ for \emph{calm}), our point is not to
interpret this too far, but to show that there are large varations even with one
area  (perceiving emotions).

@@

\fixme{TBD}
\fixme{Chek si il faut modifier les resultats de la symmetries}

@@

This study investigated the effect of a collaboration script on collaborative
learning~\citep{molinari2008effects}. The script chosen is a {\sc jigsaw}: two students
receive different but complementary subsets of the knowledge (texts) which have
to be integrated to build a shared concept map.  This script increases the
cognitive effort to build the map, not only to recon ciliate the viewpoints of
each team members but, before that, to find out what the other knows.

@@

The instructional material consisted of an explanatory text about the
neurophysiologic phenomenon of \emph{action potential}. The text was divided
into 3 chapters. The peers were located in two rooms equipped with the same
computer.  The experimental session lasted around 90 minutes and consisted of 6
phases: Participants used two software components, {\sc
CmapTools}\footnote{\url{http://cmap.ihmc.us/}} and {\sc
TeamSpeak}\footnote{\url{http://www.goteamspeak.com/}}.

@@

    \item As a pre-test, participants were asked to write down all they knew
        about the neuron and its functioning (5 minutes).

    \item Participants were instructed to read a text (12 minutes).

    \item Participants were asked to build individually a concept map in order to
        graphically represent what they learnt from the text (10 minutes).

    \item Dyads had to built a concept map during 20 minutes, communicating by
        audio.  The screen layout was structured into three areas (see Figure 8)

    \item Participants were invited to individually complete a knowledge test
        (15-20 minutes).

@@

Fifty-eight first year students from EPFL, 47 men and 11 women, with a mean age
of 20.46 were remunerated for participation. Dyads were randomly assigned to one
of the two experimental conditions. The men/women ratio was equivalent in each
condition. Participants did not know each other before the experiment. Students
from Life Sciences were not recruited since they had too high background
knowledge on the learning domain.

@@

The independent variable, script versus no-script, was implemented by the
difference of texts that individuals had to read. In the \emph{same information}
(SI) condition, the same text was given to both partners. In the
\emph{complementary information} (CI) condition, it was divided into two
sub-texts, one about the electrical processes of the neuron while the second one
about the chemical processes. These two versions were equivalent in terms of
number of information pieces.

The dependent variables were the post-test scores, but this paper is mostly
concerned by the \Model{A}{B}{knowledge}. In phase 6, participants were ask to
estimate (7-point Likert scale) their own and their partner's outcome knowledge
with respect to each chapter of the \fixme{zexz}. The order of questions about
oneself and about the other was counterbalanced across participants. We measure
\gModel{A}{B} in an objective (Eq.~\ref{eq:study4.1} and \ref{eq:study4.2}) as
well as in a subjective way (Eq.~\ref{eq:study4.3}).\fixme{check  subjective
assess: 2nd equation?}

@@

\paragraph{Grounding criterion} In this task, the grounding criterion was low,
but we did not evaluate task performance (\eg the quality of the jointly
produced concept map) but the learning gains. The correlation between
\gModel{A}{B} and $A$'s learning gains is not significant ($\beta =.08, ,NS, N =
60$). It is also not significant within each condition.

\paragraph{Study-specific questions} We performed a non-parametric Mann-Whitney
test on post-test scores for electric questions and a one-way ANOVA on scores
for ionic questions (Levene tests for homogeneity of variances: $p = .02$ and
$ns$, respectively. Results  did not show any significant difference between the
\emph{same information} (SI) condition and the \emph{complementary information}
(CI) condition, neither for electric questions [$U = 388.50, z = -0.88, ns$] nor
for ionic questions [$F(1, 58) = 0.17, ns$].  The effect of scripts on
\gModel{A}{B} was not significant ($F(1, 58) = 0.78, ns$) when considering the
absolute difference between \gModel{A}{B} and $B$'s post-test score. However, A
tended underestimate $B$'s score in the SI condition ($M = -2.06$) and to
overestimate it in the CI condition ($M = 1.21$) ($F(1, 58) = 6.44, p<.01$).
Regarding to \gModel{A}{A}, there was no significant difference between
conditions.

\paragraph{Symmetry question} The interclass correlation between \gModel{A}{B}
and \Model{B}{A} is not significant, but almost ($r=.26, F(1,29)=1.71, p=
0.075$).  Actually, it is significant when students read the same text (SI
condition: $r=0.43, F(1,15)=2.53, p<.05$) but not when they read different texts
($r=.13, F(1,12)=1.3, NS$).

\paragraph{Triangle questions} Triangle questions do not apply here since we
worked with dyads.

\paragraph{Rectangle question}$\Delta_4$: the correlation between \gmodel{A}{A}
and \gmodel{A}{B} is globally not significant ($r=0.05$) as well as not
significant in each condition: someone good at self-modelling is not necessarily
good at modelling someone else and vice-versa.

@@

In this experiment, the symmetry of mutual modelling is only found when subjects
are in conditions of symmetry of information. This consolidates the hypothesis
of \gModel{A}{B} being a property of interactions in context rather than $A$'s
cognitive attitude.

@@

It started with the same two steps as in study 4, followed by:

@@

Sixty-four first year EPFL students (18 women, mean age = 21.2 years)
participated to the study. They were involved in curricula that do not imply
advanced neurophysiologic notions. They were randomly assigned to conditions and
did not know each other before.

@@

\paragraph{Grounding criterion} A linear regression revealed a positive relation
between \gModel{A}{B} and the collaborative learning gain of the pair $\{A,
B\}$: $\beta= .401, p < .001, r2adj. =.15$, large effect. This relationship was
not significant in the previous experiment which as been conducted with the same
task: using the same task should produce the same grounding criterion. This
probably due to the fact that \gModel{A}{B} was influenced by the KAT.

\paragraph{Study-specific questions} The $t$-test reported a significant
difference between the KAT condition participants ($M = 13.4\%$) and the control
group [$M = 3.6\%, t(1, 60) = 2.73, p < .01$, Cohen's $d = 0.7$, medium to large
effect]. Providing learners with cues about the prior-knowledge of their partner
enhances their collaborative learning. As a treatment check, we found a positive
and significant correlation between the amount of gazes on KAT (using eye
tracking devices) and the learning gains ($r(22) = .54, p = .01$). A detailed
analysis revealed that subjects look at KAT to assess their peer's credibility
when (s)he provided new information.

@@

\paragraph{Symmetry question} We did not find an intra-pair correlation ($ICC =
0.05, NS$).

\paragraph{Rectangle question} $\Delta_4$: the correlation between \gmodel{A}{A} and \gmodel{A}{B} is
\fixme{???  MIRWEIS A FAIRE}.

>>>>

\listoffixmes

@@

We can go further by comparing self- versus other modelling ($\Delta_4$ in
Fig.~\ref{mm_rectangle}) as an indication of meta-cognitive skills. We can also
question if modelling skills depend upon what aspects are being modeled ($X$ or
$Y$), which would explain vertical differences ($\Delta_5$ in
Fig.~\ref{mm_rectangle}). When possible, we will also discuss these two
questions in the studies presented hereafter.

@@

We studied the impact of an awareness tool on group performance and mutual
modelling~\citep{nova2007collaboration}. The availability
of an awareness tool was our independent variable. In previous studies, we
replayed a video of the game to subjects who surprised us by their ability to
remember former states of their mutual model: ``I did that because I thought that
you would do that''. Hence, this experiment focused the representation of each
other's action plans. During the game, we asked them to anticipate the next
action of their partner as well as to announce their own actions.

@@

\begin{figure*}
        \centering
        \includegraphics[width=0.9\textwidth]{image4.png}
        \caption{Screenshot of the {\sc SpaceMiners} game}
        \label{study1:spaceminer}
\end{figure*}

{\sc SpaceMiners} is a 3D game that involves two players collecting minerals located
in asteroids (Fig.~\ref{study1:spaceminer}). To do so, they must launch drones through
the space after choosing their initial direction and speed. Once launched, the
trajectory of drones is only influenced by the gravity of planets and by
trajectory modification tools.  During the experiment, the teams were confronted
with three increasingly complex situations. The experiment was 2 hours long: a
30 minutes tutorial and 3 levels of 30 minutes. Players uses using a regular
joystick and communicated with each other through an audio channel.

@@

Thirty-six persons participated in this study, all native French speakers. We
constituted 18 dyads who did not know each other beforehand. The pairs were
randomly assigned to either the control condition (without the awareness tool)
or the awareness condition (with the awareness tool).

@@

Task performance was measured by the score reached by the two subjects at the
end of the game (three levels). The effort of mutual modelling was measured as
the ratio of time that players would spend in the scout mode (divided by total
time), which is the time during which players are not performing their own
actions but monitoring their partner's actions.

In order to evaluate \gModel{A}{B} during the task, we used two questionnaires
(Fig.~\ref{study1:questionnaires}) that were displayed during each of the three
games, as a transparent layer appearing over the game display. The first
questionnaire concerned the player's intended actions. The second questionnaire
asked each player about what he thought her or his partner was intending to do.
Some answers were identical in both questionnaires (like ``adjusting a shot'')
while others were reversed (``to guide my partner'' versus ``to guide me''). We
chose a subjective measure of accuracy ($\Delta(\M{A}{A}{X}, \M{A}{B}{X})$)
rather than an objective measure (\ie the model \gmodel{A}{B} is compared to $B$'s
next action) because some of the activities proposed by the questionnaire were not
observable by the environment (\eg establishing a strategy). We calculated
\Model{A}{B}{activity_{game_{i}}}) as the number of common answers between
questionnaires \gmodel{A}{A} and \gmodel{A}{B} in each game and computed the
average value a across the 3 levels.

@@

\paragraph{Study-specific questions} The awareness tool permitted higher group
performance, but it did not improve the accuracy of the mutual model. Since
teams were free to use the awareness tool or not (the \emph{scout} mode), we
performed a post-hoc split of players depending on how much time they used it.
The split point was the mean of time spent in the scout mode and it led to the
constitution of two groups made up of 12 individuals ``short time in scout
mode'' and 24 individuals ``long time in scout mode''\fxfatal{Inconsistent! 36
participants in awareness condition??}. A two-way analysis of
variance conducted on these contrasted groups revealed that pairs in the
awareness condition who spent more time in the scout mode reached higher levels
of \gModel{A}{B}($F = 8.02, p = 0.015$). Of course, a \textit{post-hoc} split
does not support a causal direction. An alternative explanation could be that
good modellers are more social and hence appreciate the awareness tool.

@@

@@

This study concerns a collaborative game that occurred in the physical
space~\citep{nova2006underwhelming}. We studied whether players build an accurate
model of the path followed by their partners, assuming this path reflected their
problem solving strategy. We used an objective measure of \gModel{A}{B}: the
distance between where $A$ believes $B$ has been walking and where $B$ actually went.
The main hypothesis concerned the effect of awareness tools on group performance
and on \gModel{A}{B}.

@@

{\sc CatchBob} is a mobile game in which groups of 3 players have to solve a
joint task. The game was played on EPFL campus. Participants had to find a
virtual object (\emph{Bob}) and to ``catch'' it by forming a triangle around it.
Players used a Tablet PC that displayed a map of the campus and an indication of
their personal distance to Bob. Their annotations on the map were shared with
the two other players ($A$ could see what $B$ and $C$ wrote). These annotations
faded out after a few minutes to avoid covering the full display. The awareness
tool displayed as well the location of the two other players on the map. This
resulted in three conditions: the control condition (without tool) and two
experimental conditions: synchronous awareness (display of the current position
of each player) and asynchronous awareness (display of current position of each
player as well as their recent spatial trace).

@@

Ninety EPFL students participated in this experiment. We only selected EPFL
students since knowledge of the campus geography had an impact both on group
performance and on mutual modelling: to represent the path of someone across
some space is difficult without an \textit{a priori} mental map of this space.
We formed groups of students who knew each other. We assigned 10 triads to each
of our three experimental conditions. Each condition was made up of
approximately 25\% of women, but we did not control gender repartition within
each triad.

@@

The independent variable was the presence and role of the awareness tool. As a
dependent variable, we had the task performance which was the distance covered
by the team to catch Bob and \gModel{A}{B}. To estimate \gModel{A}{B}, we asked
players to draw on paper their own path and the path of each of their partners
after the game. This enabled us to calculate the number of errors players made
while drawing the path of their partners. We compared the path that player $A$
attributed to $B$ with $B$'s real path recorded by the system and the same for
$A$ \& $C$ and $B$ \& $C$ as depicted on Fig.~\ref{study2:paths}.

@@

\paragraph{Study-specific questions} There was no significant difference
regarding the task performance. However, and surprisingly, the absence of the
awareness tool was related to a higher \gModel{A}{B}: players tended to better
remember their partners' paths when they could not constantly monitor their
positions. As detailed in the original study~\citep{nova2005location}, it
appeared that teams without awareness tool made more manual annotations on the
map while permanent monitoring has an underwhelming effect.

\paragraph{Symmetry question} The correlation between \gModel{A}{B}  and
\gModel{B}{A}  is positive ($r = .41$) and significant ($p < .01$): the more $A$
makes errors about $B$, the more $B$ does as well.

\paragraph{Triangle questions} Regarding $\Delta_2$, the correlation between
\gModel{A}{B} and \gModel{A}{C} is significant: $r=0.30, p <.01$. Concerning
$\Delta_3$, the correlation between \gModel{A}{C} and \gModel{B}{C} is
significant as well: $r=0.43, p <.001$\fxfatal{Attention! $\Delta_2$ and
$\Delta_3$ seem to be inverted! Cf fig 2}.

@@

This positive correlation observed in the symmetry question is surprising as
well: when acknowledging the high heterogeneity of spatial skills among
adults~\citep{liben1981spatial}, a significant positive correlation would
indicate that mutual modelling indeed stems from group processes more than
individual processes. The significant results on the triangle questions goes in
the same direction: either both the modeler and the modellee contribute to
accurate modelling, or the quality of teamwork has a global effect. Since team
members did not have many opportunities to directly interact during this
experiment, the factor that facilitates accurate mutual modelling is probably
more the overall group strategy than the quality of verbal interactions: a clear
strategy facilitates memorizing one's partner path.

@@

\begin{figure*}[ht!]
        \centering
        \includegraphics[width=0.8\textwidth]{image8.jpg}
        \caption{Example of argumentation graph}
        \label{study3:argumentation_graph}
\end{figure*}

@@

Triads had to address an emotional societal debate: authorizing or not adoption
by homosexual couples. They worked on-line and had to structure their
argumentation with the shared concept map tool {\sc TeamWave} as illustrated in
Fig.~\ref{study3:argumentation_graph}. Ten groups had only an audio connection
while ten groups had audio and video. The video communication was provided by a
webcam and the software {\sc IVisit}. For the audio link, we used microphones,
headsets and the {\sc BattleCom} software. In the \emph{audio plus video}
condition, the screen was divided in three sections. The main part was devoted
to the concept map window, and the images of the two peers appeared next to it.
In the audio condition, this video zone was left empty so that the size of the
concept map was equal in each condition. The subjects were located in the same
room, separated by mobile walls. Despite their headsets, non-verbal audio cues
(\eg tapping the floor with feet) were possibly heard by the participants. The
task lasted in average 61 minutes.

@@

Sixty students (twenty triads) from the University of Geneva participated to
this experiment (36 women and 24 men). We formed groups of subjects who knew
each other: the task required the discussion of sensitive issues which required
to feel quite comfortable with peers. Since groups were formed \textit{a
priori}, we did not balance gender in each condition.

@@

The independent variable was the presence or not of video link. The dependent
variable \gModel{A}{B} was measured subjectively from three questionnaires: in the first
one, $A$ described his/her own emotions \gmodel{A}{A}, while in the two other
questionnaire, $A$ described $B$'s and C's emotions. The questionnaire included 18
items (7-point Likert Scale) describing emotions labeled as adjectives:
\emph{anxious}, \emph{enthusiastic}, \emph{agitated}, \emph{proud},
\emph{excited}, \emph{quiet}, \emph{calm}, \emph{stressed}, \emph{bored},
\emph{upset}, \emph{relaxed}, \emph{irritated}, \emph{determined},
\emph{hostile}, \emph{active}, etc. \gmodel{A}{B} was modelled as a vector
of 18 numerical values corresponding to their answers on each
questionnaire items, and \gModel{A}{B} was computed as the correlation between the
two vectors \gmodel{A}{B} and \gmodel{B}{B}.

@@

\paragraph{Grounding criterion} The maps produced by teams were
ranked\fxfatal{How are they ranked?}. We used
the average rank as a estimation of the team performance and correlated it with the
average of the 6 values of \gModel{A}{B} per team (\gModel{A}{B}, \gModel{A}{C},
\gModel{B}{A},...): The correlation is -0.22 \fxfatal{p value?}: teams with a good \gModel{A}{B}
team to be better ranked.

@@

\paragraph{Triangle questions} \fixme{Check ($\Delta_2$)} For $\Delta_3$, if we
compute for each subject A, the correlation between the vectors of emotions in
\gmodel{B}{A} and the vector in \gmodel{C}{A}, and take the average across all
60 subjects, we obtain a high correlation of .66. This average is
about the same in the two conditions.

\paragraph{Rectangle question} We cannot address the relationship ($\Delta_4$)
between self-and social accuracy here because we don't have an estimation of
self-accuracy: subjects describe their emotions but we have no way to check if
there are correct. However, by measuring \gModel{A}{B} on  18 emotional labels,
we can however have a glimpse about $\Delta_5$: how \Model{A}{B}{X} varies
according to X.  Fig.~\ref{study3:deg_m_values} shows the range of modelling
errors: the difference between \gmodel{A}{B} and \gmodel{B}{B}, on a scale of 7,
is in average of 0.3 for the emotion \emph{discasted}, and up to 1.9 for the
emotion \emph{calm}. This is probably specific to the variety of scales  ($SD=
0-5$ for \emph{discated} versus $SD=.7$ for \emph{calm}), our point is not to
interpret this too far, but to show that there are large variations even with one
area  (perceiving emotions)\fxfatal{Paragraph to rewrite}.

@@

\fixme{TBD}
\fixme{Check si il faut modifier les resultats de la symmetries}

@@

This study investigated the effect of a collaboration script on collaborative
learning~\citep{molinari2008effects}. The script chosen is a {\sc jigsaw}: two students
receive different but complementary subsets of the knowledge (texts) which have
to be integrated to build a shared concept map.  This script increases the
cognitive effort to build the map, not only to conciliate the viewpoints of
each team members but, before that, to find out what the other knows.

@@

The instructional material consisted of an explanatory text about the
neurophysiologic phenomenon of \emph{action potential}. The text was divided
into 3 chapters.  In the \emph{same information} (SI) condition, the same text
was given to both partners. In the \emph{complementary information} (CI)
condition, it was divided into two sub-texts, one about the electrical processes
of the neuron while the second one about the chemical processes. These two
versions were equivalent in terms of number of information pieces.

The peers were located in two rooms equipped with the same
computer.  The experimental session lasted around 90 minutes and consisted of 6
phases: Participants used two software components, {\sc CmapTools} and {\sc
TeamSpeak}.

@@

    \item As a pre-test, participants were asked to write down all they knew
        about the neuron and its functioning (5 minutes),

    \item Participants were instructed to read a text (12 minutes),

    \item Participants were asked to build individually a concept map in order to
        graphically represent what they learnt from the text (10 minutes),

    \item Dyads had to built a concept map during 20 minutes, communicating by
        audio.  The screen layout was structured into three areas
        (Fig.~\ref{study4:concept_map}),

    \item Participants were invited to individually complete a knowledge test
        (15-20 minutes),

@@

Fifty-eight first year students from EPFL (47 men and 11 women, mean age: 20.46)
were remunerated for participation. Dyads were randomly assigned to one of the
two experimental conditions. Gender was balanced over the conditions.
Participants did not know each other before the experiment. Students from Life
Sciences faculty were not recruited to avoid high initial background knowledge on the
learning domain.

@@

The independent variable, script versus no-script, was implemented by the
difference of texts that individuals had to read.  The dependent variables were
the post-test scores, used to assess \Model{A}{B}{knowledge}. In phase 6,
participants were ask to estimate (7-point Likert scale) their own and their
partner's outcome knowledge with respect to each chapter of the learning
material. The order of questions about oneself and about the other was
counterbalanced across participants. We measure \gModel{A}{B} in an objective
(Eq.~\ref{eq:study4.1} and \ref{eq:study4.2}) as well as in a subjective way
(Eq.~\ref{eq:study4.3}).

@@

\paragraph{Grounding criterion} In this task, the grounding criterion was low.
We did not however evaluate task performance (\eg the quality of the jointly
produced concept map) but learning gains. The correlation between \gModel{A}{B}
and $A$'s learning gains is not significant ($\beta =.08, ns, N = 60$). It is
also not significant within each condition.

\paragraph{Study-specific questions} We performed a non-parametric Mann-Whitney
test on post-test scores for electric questions and a one-way ANOVA on scores
for ionic questions (Levene tests for homogeneity of variances): $p = .02$ and
$ns$, respectively. Results  did not show any significant difference between the
\emph{same information} (SI) condition and the \emph{complementary information}
(CI) condition, neither for electric questions [$U = 388.50, z = -0.88, ns$] nor
for ionic questions [$F(1, 58) = 0.17, ns$].  The effect of scripts on
\gModel{A}{B} was not significant ($F(1, 58) = 0.78, ns$) when considering the
absolute difference between \gModel{A}{B} and $B$'s post-test score. However, A
tended underestimate $B$'s score in the SI condition ($M = -2.06$) and to
overestimate it in the CI condition ($M = 1.21$) ($F(1, 58) = 6.44, p<.01$).
Regarding to \gModel{A}{A}, there was no significant difference between
conditions.

\paragraph{Symmetry question} The inter-class correlation between \gModel{A}{B}
and \gModel{B}{A} is approaching significance ($r=.26, F(1,29)=1.71, p=
0.075$). It is indeed significant when students read the same text (SI
condition: $r=0.43, F(1,15)=2.53, p<.05$) but not when they read different texts
($r=.13, F(1,12)=1.3, ns$).

\paragraph{Rectangle question} The correlation between \gmodel{A}{A}
and \gmodel{A}{B} ($\Delta_4$) is globally not significant ($r=0.05$) as well as not
significant in each condition: someone good at self-modelling is not necessarily
good at modelling someone else and vice-versa.

@@

In this experiment, the symmetry of mutual modelling is only found when subjects
are in conditions of symmetry of information. This consolidates the hypothesis
of \gModel{A}{B} being a property of interactions in context rather than $A$'s
cognitive attitude\fxfatal{to be better justified}.

@@

It started with the same two first steps as in study 4, followed by:

@@

Sixty-four first year EPFL students (46 men, 18 women, mean age: 21.2)
participated to the study. They were randomly assigned to conditions and
did not know each other before. Like in Study 4, students from Life Science
faculty were excluded.

@@

\paragraph{Grounding criterion} A linear regression revealed a positive relation
between \gModel{A}{B} and the collaborative learning gain\fxfatal{What is the
collaborative learning gain} of the pair $\{A,
B\}$: $\beta= .401, p < .001, r2adj. =.15$, large effect. This relationship was
not significant in the previous experiment which as been conducted with the same
task: using the same task should produce the same grounding criterion. This
probably due to the fact that \gModel{A}{B} was influenced by the KAT.

\paragraph{Study-specific questions} The $t$-test reported a significant
difference between the KAT condition participants ($M = 13.4\%$) and the control
group [$M = 3.6\%, t(1, 60) = 2.73, p < .01$, Cohen's $d = 0.7$, medium to large
effect]: providing learners with cues about the prior-knowledge of their partner
enhances their collaborative learning. As a treatment check, we found a positive
and significant correlation between the amount of gazes on KAT (using eye
tracking devices) and the learning gains ($r(22) = .54, p = .01$). A detailed
analysis revealed that subjects look at KAT to assess their peer's credibility
when he/she provided new information.

@@

\paragraph{Symmetry question} We did not find an intra-pair correlation ($ICC =
0.05, ns$).

%\paragraph{Rectangle question} $\Delta_4$: the correlation between \gmodel{A}{A} and \gmodel{A}{B} is
%\fixme{???  MIRWEIS A FAIRE}.
